---
title: "R Notebook"
output: html_notebook
---

Indlæs biblioteker

```{r}
library(ggplot2)
library(tidyr)
library(dplyr)
```

Skriv tau ned

```{r}
tau <- c(0.01,0.015,0.02,0.025,0.03,0.035,0.04,0.045,0.05,0.055,0.06,0.065,0.07,0.075,0.08,0.085,0.09,0.095,0.1)
```

# Profit per væddemål fordeling

```{r}
plot_tau_vs_profit <- function(tau, profit_home, profit_draw, profit_away, model_name = "Model") {

  df <- data.frame(
    tau = tau,
    Hjemmesejr = profit_home,
    Uafgjort = profit_draw,
    Udebanesejr = profit_away
  )

  df_long <- pivot_longer(df, cols = -tau, names_to = "Resultat", values_to = "Profit")

  p <- ggplot(df_long, aes(x = tau, y = Profit, color = Resultat, shape = Resultat)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2.5) +
    scale_color_manual(values = c("blue", "red", "darkgreen")) +
    labs(title = paste("Profit per væddemål vs. τ —", model_name),
         x = expression(tau),
         y = "Profit per væddemål") +
    theme_minimal(base_size = 13) +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"),
          legend.position = "top") + coord_cartesian(ylim = c(-20,40))
  

  print(p)
}
```

## CatBoost Premier League

```{r}
profit_home_CB <- c(0.00, -1.73, 1.24, -0.65, -1.86, -0.18, 2.34, 2.88, 5.86,
                 2.59, -0.16, -0.82, -2.81, -2.32, -6.11, -7.85, -4.19, -5.21, 1.30)
profit_draw_CB <- c(-4.97, -6.75, -5.54, -2.25, 2.72, 8.02, 7.86, 16.01, 23.70,
                 0.50, 12.41, 17.95, 5.99, -5.48, -18.78, 36.29, 55.38, 102.46, 150.22)
profit_away_CB <- c(13.04, 7.52, 12.49, 8.66, 11.33, 2.19, 5.64, 8.20, 7.65,
                 7.03, 7.14, 11.94, 10.14, 11.12, 9.36, 12.53, 4.78, 5.79, 8.80)
plot_tau_vs_profit_gg(tau, profit_home_CB, profit_draw_CB, profit_away_CB, model_name = "CatBoost")
```

## LightGBM Premier League

```{r}
profit_home_LG <- c(5.96, 7.26, 3.57, 4.12, 3.92, 0.04, -3.45, -5.15, -4.53, -5.87, -5.98, -5.49, -4.09, 1.06, 0.47, -0.58, 1.78, -0.2, 0.98)
profit_draw_LG <- c(-3.54, 0.19, -4.41, -8.74, -12.53, -13.82, -14.76, 0.82, 4.37, -10.22, 8.00, 27.07, 30.74, 38.71, 69.19, 8.43, -25.62, -6.35, 6.97)
profit_away_LG <- c(13.73, 8.34, 6.01, 1.21, 3.97, 3.78, 6.98, 9.92, 10.79, 13.10, 16.06, 21.41, 27.47, 34.22, 35.01, 29.07, 25.65, 24.29, 19.68)

plot_tau_vs_profit(tau, profit_home_LG, profit_draw_LG, profit_away_LG, model_name = "LightGBM")
```

## Linear Regression Premier League

```{r}
profit_home_LR <- c(1.07, 3.03, -0.71, -1.85, -1.01, -0.29, 2.49, -0.49, 3.48, 2.82, 3.15, 4.04, 8.37, 6.88, 2.89, 6.25, 10.06, 8.6, 6.65)
profit_draw_LR <- c(-1.86, -1.32, 3.93, 4.73, 4.72, 4.99, 6.82, 8.37, 13.99, 8.59, 9.59, 9.73, 3.28, 29.78, 31.41, 42.38, 54.05, 33.33, 19.81)
profit_away_LR <- c(14.05, 14.79, 11.95, 9.41, 14.58, 16.07, 16.61, 17.21, 13.32, 4.95, 8.22, 9.85, 16.83, 19.28, 16.01, 6.86, 6.6, 7.49, -0.88)

plot_tau_vs_profit(tau, profit_home_LR, profit_draw_LR, profit_away_LR, model_name = "Linear Regrssion")
```

## Neural Network Premier League

```{r}
profit_home_NN <- c(0, -1.73, 1.24, -0.65, -1.86, -0.18, 2.34, 2.88, 5.86, 2.59,
                 -0.16, -0.82, -2.81, -2.32, -6.11, -7.85, -4.19, -5.21, 1.3)

profit_draw_NN <- c(-4.97, -6.75, -5.54, -2.25, 2.72, 8.02, 7.86, 16.01, 23.7, 0.5,
                 12.41, 17.95, 5.99, -5.48, -18.78, 36.29, 55.38, 102.46, 150.22)

profit_away_NN <- c(13.04, 7.52, 12.49, 8.66, 11.33, 2.19, 5.64, 8.2, 7.65, 7.03,
                 7.14, 11.94, 10.14, 11.12, 9.36, 12.53, 4.78, 5.79, 8.8)

plot_tau_vs_profit(tau, profit_home_NN, profit_draw_NN, profit_away_NN, model_name = "Neural Network")

```

## Random Forest Premier League

```{r}
profit_home_RF <- c(3.78, 2.48, 1.93, 0.43, -1.57, -5.12, -8.14, -9.85, -7.96, -6.92, -4.72, -3.37, -0.82, -3.38, -0.77, 1.24, 1.25, 4.11, 5.92)
profit_draw_RF <- c(-3.97, -7.64, -10.46, -5.11, -14.33, -15.89, -22.06, -36.76, -24.49, -7.81, 3.23, 8.14, 16.49, 29.66, 39.89, 28.77, -3.62, -25.62, -6.35)
profit_away_RF <- c(10.29, 8.41, 4.18, 8.29, 14.25, 10.56, 13.76, 7.94, 7.53, 10.98, 8.59, 8.28, 11.4, 13.9, 15.18, 18.85, 12.04, 18.12, 19.81)

plot_tau_vs_profit(tau, profit_home_RF, profit_draw_RF, profit_away_RF, model_name = "Random Forest")
```

## XGBoost Premier League

```{r}
profit_home_XG <- c(3.78, 2.48, 1.93, 0.43, -1.57, -5.12, -8.14, -9.85, -7.96, -6.92, -4.72, -3.37, -0.82, -3.38, -0.77, 1.24, 1.25, 4.11, 5.92)
profit_draw_XG <- c(-3.97, -7.64, -10.46, -5.11, -14.33, -15.89, -22.06, -36.76, -24.49, -7.81, 3.23, 8.14, 16.49, 29.66, 39.89, 28.77, -3.62, -25.62, -6.35)
profit_away_XG <- c(10.29, 8.41, 4.18, 8.29, 14.25, 10.56, 13.76, 7.94, 7.53, 10.98, 8.59, 8.28, 11.4, 13.9, 15.18, 18.85, 12.04, 18.12, 19.81)

plot_tau_vs_profit(tau, profit_home_XG, profit_draw_XG, profit_away_XG, model_name = "XGBoost")
```

## CatBoost Bundesligsa

```{r}
profit_home_BCB <- c(13.92, 16.44, 17.52, 21.41, 21.32, 24.28, 26.33, 25.53, 23.79, 18.65, 23.88, 23.59, 27.26, 25.4, 23.34, 26.58, 28.04, 30.41, 28.73)
profit_draw_BCB <- c(3.02, 5.96, 3.11, 4.92, -0.29, -6.94, -18.93, -18.86, -7.95, -5.41, 19.17, 26.44, 20.38, 30.31, 31.07, 119.79, 226.66, 226.66,0)
profit_away_BCB <- c(-11.44, -10.29, -5.88, -4.73, -6.0, -0.61, -1.44, -3.8, 2.4, 4.26, -3.87, 6.25, -4.92, -2.96, -2.59, 4.5, 6.92, 14.59, -1.54)

plot_tau_vs_profit(tau, profit_home_BCB, profit_draw_BCB, profit_away_BCB, model_name = "CatBoost")
```

## LightGBM Bundesligsa

```{r}
profit_home_BLG <- c(13.69, 15.1, 16.97, 18.14, 19.86, 23.44, 21.48, 24.5, 27.09, 17.02, 21.78, 25.49, 30.36, 24.4, 25.23, 28.1, 38.85, 27.31, 22.52)
profit_draw_BLG <- c(0.86, 2.59, 8.34, 19.69, 17.37, 16.23, 7.92, -2.61, 3.73, 11.53, 22.32, 1.76, 34.66, 90.25, 226.66, 226.66, 226.66, 226.66, -100.0)
profit_away_BLG <- c(-11.23, -11.96, -9.03, -7.58, -10.63, -7.68, -4.85, -16.06, -11.95, -6.39, -1.23, -0.48, 3.9, 6.43, -0.25, 5.94, 13.99, 24.42, 10.16)

plot_tau_vs_profit(tau, profit_home_BLG, profit_draw_BLG, profit_away_BLG, model_name = "LightGBM")
```

## Linear Regression Bundesligsa

```{r}
profit_home_BLR <- c(8.18, 8.96, 12.4, 10.73, 9.81, 14.41, 13.45, 12.95, 9.02, 13.91, 9.79, 13.7, 10.74, 13.78, 11.17, 11.33, 10.22, 11.55, 17.9)
profit_draw_BLR <- c(-3.29, -10.32, -12.42, -8.47, -6.82, -5.93, 10.53, 1.5, 6.09, 6.74, 19.85, 21.47, 28.08, 59.9, 14.79, 50.08, 50.08, 48.75, 91.01)
profit_away_BLR <- c(-9.31, -8.62, -9.59, -13.52, -12.62, -16.46, -18.61, -15.36, -15.67, -10.37, -3.52, -20.24, -15.51, -11.26, -4.49, -5.3, -15.7, -11.92, -7.1)

plot_tau_vs_profit(tau, profit_home_BLR, profit_draw_BLR, profit_away_BLR, model_name = "Linear Regression")
```

## Neural Network Bundesligsa

```{r}
profit_home_BNN <- c(10.64, 10.93, 8.90, 8.92, 11.04, 15.13, 15.35, 14.81, 16.48, 14.91, 14.49, 16.64, 23.63, 26.13, 20.42, 18.68, 19.49, 13.07, 17.86)
profit_draw_BNN <- c(2.99, 10.13, 5.29, 2.24, 6.35, 6.48, 11.06, 12.47, 19.54, 44.31, 40.22, 32.99, 43.89, 116.28, 158.58, 217.10, 330.21, 330.21, 550.00)
profit_away_BNN <- c(-11.79, -10.40, -9.36, -8.98, -12.79, -11.50, -5.19, -6.76, -4.37, -1.51, -0.61, 8.07, 11.03, 10.30, 4.55, -14.25, -13.59, -13.94, -16.31)

plot_tau_vs_profit(tau, profit_home_BNN, profit_draw_BNN, profit_away_BNN, model_name = "Neural Network")
```

## Random Forest Bundesligsa

```{r}
profit_home_BRF <- c(15.75, 17.90, 18.79, 17.62, 18.58, 19.98, 23.33, 21.30, 25.87, 29.46, 35.26, 24.63, 25.32, 19.93, 17.58, 20.57, 27.15, 30.06, 31.21)
profit_draw_BRF <- c(11.78, 6.52, 1.98, 6.53, 13.54, -6.13, -12.98, -9.26, -5.40, 6.94, 18.72, 22.83, 21.58, 4.63, 7.21, -17.83, 31.07, 119.79, -100.00)
profit_away_BRF <- c(-8.12, -8.74, -16.73, -18.85, -15.18, -14.80, -14.73, -9.80, -15.70, -16.12, -12.58, -11.70, -3.93, -0.45, -0.83, -3.62, -4.81, -13.37, -27.54)

plot_tau_vs_profit(tau, profit_home_BRF, profit_draw_BRF, profit_away_BRF, model_name = "Random Forest")
```

## XGBoost Bundesligsa

```{r}
profit_home_BXG <- c(12.98, 13.08, 16.19, 17.42, 20.61, 21.84, 21.57, 23.49, 20.79, 21.29, 19.25, 25.13, 32.18, 32.11, 26.97, 25.16, 31.10, 22.93, 22.71)
profit_draw_BXG <- c(1.06, 4.50, 4.05, 15.05, 17.52, -8.22, -7.76, 1.01, 8.53, 22.99, 22.80, 31.54, 5.48, 111.51, 65.49, 226.66, 226.66, 226.66, 550.00)
profit_away_BXG <- c(-12.90, -12.09, -9.51, -6.37, -8.63, -7.48, -6.15, -7.48, -11.05, -6.85, -1.19, 2.57, 0.00, 3.02, 0.11, 10.06, 17.42, 25.67, 17.07)

plot_tau_vs_profit(tau, profit_home_BXG, profit_draw_BXG, profit_away_BXG, model_name = "XGBoost")
```

# Overskud procent fordeling

```{r}
plot_tau_vs_overskud <- function(tau, overskud_home, overskud_draw, overskud_away, model_name = "Model") {
  df <- data.frame(
    tau = tau,
    Hjemmesejr = overskud_home,
    Uafgjort = overskud_draw ,
    Udebanesejr = overskud_away
  )

  df_long <- tidyr::pivot_longer(df, cols = -tau, names_to = "Resultat", values_to = "Overskud")

  ggplot(df_long, aes(x = tau, y = Overskud, color = Resultat, shape = Resultat)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2.5) +
    scale_color_manual(values = c("blue", "red", "darkgreen")) +
    labs(title = paste("% Overskud vs. τ —", model_name),
         x = expression(tau),
         y = "% Overskud ift. 50%") +
    theme_minimal(base_size = 13) +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"),
          legend.position = "top") +
    coord_cartesian(ylim = c(0, 100))
}
```

## CatBoost Premier League

```{r}
overskud_home_CB <- c(49.60, 38.87, 56.46, 45.69, 39.26, 48.78, 60.70, 62.76, 74.31,
                   60.92, 48.99, 45.42, 38.70, 40.58, 29.30, 25.33, 36.71, 35.13, 52.68)
overskud_draw_CB <- c(23.23, 18.81, 25.51, 39.97, 59.26, 72.47, 69.31, 81.27, 85.84,
                   48.91, 66.50, 70.97, 54.38, 39.24, 33.36, 60.46, 76.13, 84.86, 70.63)
overskud_away_CB <- c(92.32, 79.63, 90.45, 82.12, 86.99, 58.53, 70.74, 77.41, 74.17,
                   71.28, 70.79, 80.11, 76.07, 75.81, 71.76, 76.61, 60.03, 60.60, 65.53)
plot_tau_vs_overskud(tau, overskud_home_CB, overskud_draw_CB, overskud_away_CB, model_name = "CatBoost")
```

## LightGBM Premier League

```{r}
overskud_home_LG <- c(82.15, 85.86, 69.51, 71.73, 70.72, 49.72, 30.74, 23.01, 27.32, 21.94, 22.52, 25.14, 31.79, 53.44, 50.78, 47.25, 56.14, 48.41, 52.84)
overskud_draw_LG <- c(34.26, 50.09, 33.95, 23.22, 17.15, 18.1, 18.27, 50.87, 56.09, 32.97, 59.02, 77.11, 75.85, 75.47, 80.45, 53.48, 26.3, 26.77, 66.31)
overskud_away_LG <- c(94.38, 82.95, 75.53, 54.15, 66.20, 65.38, 75.63, 82.31, 83.33, 85.96, 90.31, 95.07, 97.40, 98.96, 98.46, 97.21, 94.29, 93.44, 86.91)

plot_tau_vs_overskud(tau, overskud_home_LG, overskud_draw_LG, overskud_away_LG, model_name = "LightGMB")
```

## Linear Regression Premier League

```{r}
overskud_home_LR <- c(56.09, 67.84, 45.77, 38.42, 43.06, 47.95, 62.61, 46.81, 67.6, 63.34, 64.82, 67.9, 81.05, 75.3, 60.41, 69.97, 78.22, 73.0, 67.1)
overskud_draw_LR <- c(41.97, 44.52, 62.66, 64.0, 63.42, 62.45, 66.16, 68.0, 76.77, 65.62, 66.06, 64.74, 53.0, 81.62, 80.59, 85.83, 88.79, 73.95, 58.97)
overskud_away_LR <- c(94.35, 93.92, 89.88, 82.6, 92.23, 93.53, 94.04, 94.87, 89.27, 66.72, 75.05, 77.89, 88.82, 90.38, 84.94, 66.15, 64.93, 66.61, 46.36)

plot_tau_vs_overskud(tau, overskud_home_LR, overskud_draw_LR, overskud_away_LR, model_name = "Linear Regression")
```

## Neural Network Premier League

```{r}
overskud_home_NN <- c(49.60, 38.87, 56.46, 45.69, 39.26, 48.78, 60.70, 62.76, 74.31,
                   60.92, 48.99, 45.42, 38.70, 40.58, 29.30, 25.33, 36.71, 35.13, 52.68)

overskud_draw_NN <- c(23.23, 18.81, 25.51, 39.97, 59.26, 72.47, 69.31, 81.27, 85.84,
                   48.91, 66.50, 70.97, 54.38, 39.24, 33.36, 60.46, 76.13, 84.86, 70.63)

overskud_away_NN <- c(92.32, 79.63, 90.45, 82.12, 86.99, 58.53, 70.74, 77.41, 74.17,
                   71.28, 70.79, 80.11, 76.07, 75.81, 71.76, 76.61, 60.03, 60.60, 65.53)


plot_tau_vs_overskud(tau, overskud_home_NN, overskud_draw_NN, overskud_away_NN, model_name = "Neural Network")

```

## Random Forest Premier League

```{r}
overskud_home_RF <- c(72.35, 65.03, 60.23, 52.1, 40.15, 22.02, 12.08, 7.76, 13.57, 17.82, 27.51, 33.25, 45.17, 34.34, 46.4, 54.94, 54.49, 64.72, 69.13)
overskud_draw_RF <- c(32.51, 21.3, 16.7, 32.92, 13.41, 13.24, 8.54, 1.67, 10.45, 35.98, 53.02, 57.46, 60.37, 72.22, 75.64, 60.52, 39.79, 26.3, 26.77)
overskud_away_RF <- c(87.39, 81.59, 67.71, 80.88, 92.6, 87.3, 91.85, 79.03, 76.52, 84.31, 79.54, 76.93, 82.68, 86.71, 87.46, 90.41, 78.93, 87.29, 87.65)

plot_tau_vs_overskud(tau, overskud_home_RF, overskud_draw_RF, overskud_away_RF, model_name = "Random Forest")
```

## XGBoost Premier League

```{r}
overskud_home_XG <- c(72.35, 65.03, 60.23, 52.1, 40.15, 22.02, 12.08, 7.76, 13.57, 17.82, 27.51, 33.25, 45.17, 34.34, 46.4, 54.94, 54.49, 64.72, 69.13)
overskud_draw_XG <- c(32.51, 21.3, 16.7, 32.92, 13.41, 13.24, 8.54, 1.67, 10.45, 35.98, 53.02, 57.46, 60.37, 72.22, 75.64, 60.52, 39.79, 26.3, 26.77)
overskud_away_XG <- c(87.39, 81.59, 67.71, 80.88, 92.6, 87.3, 91.85, 79.03, 76.52, 84.31, 79.54, 76.93, 82.68, 86.71, 87.46, 90.41, 78.93, 87.29, 87.65)

plot_tau_vs_overskud(tau, overskud_home_XG, overskud_draw_XG, overskud_away_XG, model_name = "XGBoost")
```

## CatBoost Bundesliga

```{r}
overskud_home_BCB <- c(96.28, 98.09, 98.07, 99.18, 99.05, 99.41, 99.64, 99.42, 98.33, 96.0, 97.96, 98.18, 98.99, 98.41, 97.61, 98.03, 97.89, 97.86, 96.42)
overskud_draw_BCB <- c(59.54, 67.27, 58.42, 61.4, 48.68, 35.48, 18.37, 22.76, 38.3, 42.36, 64.5, 68.19, 59.01, 62.17, 67.9, 70.63, 75.01, 75.01,0)
overskud_away_BCB <- c(11.98, 14.98, 28.57, 32.65, 29.81, 46.16, 43.8, 37.54, 53.94, 57.91, 37.4, 65.54, 34.91, 40.75, 42.27, 60.2, 64.88, 77.98, 45.35)

plot_tau_vs_overskud(tau, overskud_home_BCB, overskud_draw_BCB, overskud_away_BCB, model_name = "CatBoost")
```

## LightGBM Bundesliga

```{r}
overskud_home_BLG <- c(96.22, 97.09, 97.75, 97.89, 98.25, 99.13, 98.02, 98.95, 99.14, 96.14, 98.31, 98.92, 99.66, 98.08, 97.96, 98.5, 99.74, 95.9, 91.43)
overskud_draw_BLG <- c(52.45, 57.28, 70.73, 86.4, 81.85, 76.32, 61.76, 44.39, 52.55, 59.43, 67.06, 52.61, 67.52, 84.9, 75.01, 75.01, 75.01, 75.01, 0.0)
overskud_away_BLG <- c(11.83, 12.41, 20.05, 24.24, 17.92, 25.77, 34.06, 6.79, 14.51, 29.49, 45.15, 47.26, 59.34, 64.62, 47.65, 61.38, 76.51, 87.94, 72.45)

plot_tau_vs_overskud(tau, overskud_home_BLG, overskud_draw_BLG, overskud_away_BLG, model_name = "LightGBM")
```

## Linear Regression Bundesliga

```{r}
overskud_home_BLR <- c(84.92, 86.29, 93.22, 90.33, 89.95, 96.21, 94.42, 92.53, 83.52, 91.68, 82.88, 89.0, 82.75, 87.54, 80.8, 78.59, 74.53, 77.0, 83.02)
overskud_draw_BLR <- c(38.3, 20.21, 17.18, 27.68, 33.0, 36.65, 67.66, 50.73, 56.48, 54.9, 65.9, 61.99, 69.28, 82.27, 59.24, 68.47, 68.47, 62.15, 63.03)
overskud_away_BLR <- c(16.4, 19.64, 18.61, 12.33, 13.81, 9.46, 8.05, 14.05, 15.57, 25.49, 39.33, 6.53, 13.49, 21.83, 38.97, 37.72, 20.07, 26.98, 36.67)

plot_tau_vs_overskud(tau, overskud_home_BLR, overskud_draw_BLR, overskud_away_BLR, model_name = "Linear Regression")
```

## Neural Network Bundesligsa

```{r}
overskud_home_BNN <- c(94.48, 94.76, 90.85, 89.65, 93.30, 97.52, 97.13, 95.77, 96.70, 94.46, 93.16, 94.26, 98.44, 98.74, 97.44, 95.82, 95.79, 85.37, 91.62)
overskud_draw_BNN <- c(61.30, 81.23, 65.46, 55.81, 64.34, 62.08, 68.01, 68.76, 73.23, 86.22, 80.58, 73.89, 79.08, 93.48, 95.22, 95.30, 95.86, 95.86, 100.00)
overskud_away_BNN <- c(7.95, 11.14, 14.38, 16.64, 9.75, 13.15, 31.52, 28.26, 35.29, 44.95, 46.26, 66.96, 71.62, 68.88, 56.30, 20.28, 22.24, 22.94, 20.83)

plot_tau_vs_overskud(tau, overskud_home_BNN, overskud_draw_BNN, overskud_away_BNN, model_name = "Neural Network")
```

## Random Forest Bundesliga

```{r}
overskud_home_BRF <- c(97.70, 98.79, 98.60, 97.87, 97.82, 97.94, 98.44, 97.98, 98.94, 99.45, 99.72, 97.97, 98.00, 95.51, 92.18, 94.44, 97.16, 96.81, 95.93)
overskud_draw_BRF <- c(84.31, 68.12, 53.71, 64.15, 74.52, 37.83, 27.74, 34.62, 40.95, 55.90, 63.68, 66.86, 57.49, 59.36, 62.07, 26.87, 67.90, 70.63, 0.00)
overskud_away_BRF <- c(20.01, 19.21, 2.67, 1.98, 5.49, 6.71, 7.11, 18.34, 7.28, 6.77, 12.99, 16.01, 37.09, 47.98, 46.75, 39.75, 36.99, 19.38, 4.74)

plot_tau_vs_overskud(tau, overskud_home_BRF, overskud_draw_BRF, overskud_away_BRF, model_name = "Random Forest")
```

## XGBoost Bundesliga

```{r}
overskud_home_BXG <- c(95.43, 94.18, 96.78, 97.61, 98.71, 98.67, 98.04, 98.57, 98.03, 97.67, 97.13, 98.96, 99.67, 99.47, 98.78, 97.24, 98.62, 93.69, 91.81)
overskud_draw_BXG <- c(53.18, 62.50, 59.84, 81.04, 81.55, 32.69, 35.51, 49.66, 58.13, 70.78, 67.83, 69.00, 58.35, 85.57, 69.23, 75.01, 75.01, 75.01, 100.00)
overskud_away_BXG <- c(9.15, 11.83, 18.81, 27.54, 22.67, 26.20, 30.58, 27.74, 16.51, 28.00, 44.56, 55.85, 48.72, 55.88, 48.36, 70.38, 80.83, 89.04, 82.25)

plot_tau_vs_overskud(tau, overskud_home_BXG, overskud_draw_BXG, overskud_away_BXG, model_name = "XGBoost")
```

# CLT 95% fodeling

```{r}
plot_tau_vs_clt <- function(tau, clt_home, clt_draw, clt_away, model_name = "Model") {
  df <- data.frame(
    tau = tau,
    Hjemmesejr = clt_home,
    Uafgjort = clt_draw,
    Udebanesejr = clt_away
  )

  df_long <- tidyr::pivot_longer(df, cols = -tau, names_to = "Resultat", values_to = "CLT")

  ggplot(df_long, aes(x = tau, y = CLT, color = Resultat, shape = Resultat)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2.5) +
    scale_color_manual(values = c("blue", "red", "darkgreen")) +
    labs(title = paste("CLT 95% vs. τ —", model_name),
         x = expression(tau),
         y = "CLT 95% Nedre Grænse") +
    theme_minimal(base_size = 13) +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"),
          legend.position = "top") +
    coord_cartesian(ylim = c(-30, 15))
}
```

## CatBoost Premier League

```{r}
clt_home_CB <- c(-10.79, -12.52, -10.26, -12.09, -13.62, -12.59, -10.78, -10.79, -8.72,
              -11.69, -14.71, -16.65, -19.07, -19.70, -25.70, -27.93, -26.00, -27.81, -22.66)
clt_draw_CB <- c(-16.23, -19.20, -19.38, -17.98, -15.27, -13.18, -16.71, -13.42, -12.92,
              -36.74, -32.68, -32.91, -51.41, -70.16, -91.61, -79.78, -74.99, -59.67, -185.48)
clt_away_CB <- c(-2.26, -7.27, -3.69, -6.82, -5.21, -13.49, -11.11, -9.62, -11.13,
              -12.94, -14.21, -11.25, -13.11, -14.30, -17.25, -16.24, -24.20, -24.53, -24.92)
plot_tau_vs_clt(tau, clt_home_CB, clt_draw_CB, clt_away_CB, model_name = "CatBoost")
```

## LightGBM Premier League

```{r}
clt_home_LG <- c(-4.65, -3.80, -7.83, -7.42, -7.86, -11.47, -15.01, -16.79, -16.98, -18.46, -19.17, -19.15, -18.75, -14.41, -15.36, -17.12, -15.75, -17.86, -17.57)
clt_draw_LG <- c(-18.30, -16.59, -22.66, -28.75, -34.56, -38.39, -41.62, -32.78, -34.83, -51.92, -41.13, -33.14, -37.45, -43.52, -51.07, -107.96, -141.21, -150.30, -155.77)
clt_away_LG <- c(-0.85, -6.01, -8.08, -13.02, -10.97, -11.30, -9.12, -7.40, -7.56, -6.74, -4.52, -0.82, 3.36, 8.44, 7.15, 3.44, -1.22, -3.07, -9.17)

plot_tau_vs_clt(tau, clt_home_LG, clt_draw_LG, clt_away_LG, model_name = "LightGBM")
```

## Linear Regression Premier League

```{r}
clt_home_LR <- c(-9.12, -7.54, -11.06, -12.21, -11.66, -11.66, -9.68, -12.47, -9.0, -10.2, -10.56, -10.14, -7.09, -9.65, -14.46, -12.99, -10.98, -13.68, -16.97)
clt_draw_LR <- c(-17.51, -18.45, -15.11, -15.62, -17.19, -19.12, -18.96, -19.89, -16.4, -23.99, -26.14, -29.55, -40.37, -24.0, -27.37, -22.64, -19.61, -47.73, -69.74)
clt_away_LR <- c(-0.83, -1.1, -3.73, -6.81, -2.56, -1.84, -1.44, -0.28, -4.48, -12.87, -11.14, -11.01, -6.01, -5.25, -9.23, -18.46, -20.04, -19.63, -28.76)

plot_tau_vs_clt(tau, clt_home_LR, clt_draw_LR, clt_away_LR, model_name = "Linear Regression")
```

## Neural Network Premier League

```{r}
clt_home_NN <- c(-10.79, -12.52, -10.26, -12.09, -13.62, -12.59, -10.78, -10.79, -8.72,
              -11.69, -14.71, -16.65, -19.07, -19.70, -25.70, -27.93, -26.00, -27.81, -22.66)

clt_draw_NN<- c(-16.23, -19.20, -19.38, -17.98, -15.27, -13.18, -16.71, -13.42, -12.92,
              -36.74, -32.68, -32.91, -51.41, -70.16, -91.61, -79.78, -74.99, -59.67, -185.48)

clt_away_NN <- c(-2.26, -7.27, -3.69, -6.82, -5.21, -13.49, -11.11, -9.62, -11.13,
              -12.94, -14.21, -11.25, -13.11, -14.30, -17.25, -16.24, -24.20, -24.53, -24.92)


plot_tau_vs_clt(tau, clt_home_NN, clt_draw_NN, clt_away_NN, model_name = "Neural Network")
```

## Random Forest Premier League

```{r}
clt_home_RF <- c(-6.56, -8.04, -8.96, -10.8, -12.82, -16.29, -19.43, -21.04, -19.66, -19.13, -17.7, -16.86, -14.97, -17.37, -15.59, -14.19, -14.76, -13.13, -12.99)
clt_draw_RF <- c(-19.01, -23.89, -28.43, -25.17, -35.54, -39.55, -47.77, -63.33, -56.29, -46.55, -44.81, -46.91, -54.49, -55.73, -62.0, -81.45, -108.34, -141.21, -150.3)
clt_away_RF <- c(-4.53, -7.11, -10.49, -7.22, -2.22, -4.66, -2.49, -8.19, -9.21, -6.88, -8.4, -9.95, -8.23, -6.79, -6.73, -4.88, -12.43, -7.97, -8.19)

plot_tau_vs_clt(tau, clt_home_RF, clt_draw_RF, clt_away_RF, model_name = "Random Forest")
```

## XGBoost Premier League

```{r}
clt_home_XG <- c(-6.56, -8.04, -8.96, -10.8, -12.82, -16.29, -19.43, -21.04, -19.66, -19.13, -17.7, -16.86, -14.97, -17.37, -15.59, -14.19, -14.76, -13.13, -12.99)
clt_draw_XG <- c(-19.01, -23.89, -28.43, -25.17, -35.54, -39.55, -47.77, -63.33, -56.29, -46.55, -44.81, -46.91, -54.49, -55.73, -62.0, -81.45, -108.34, -141.21, -150.3)
clt_away_XG <- c(-4.53, -7.11, -10.49, -7.22, -2.22, -4.66, -2.49, -8.19, -9.21, -6.88, -8.4, -9.95, -8.23, -6.79, -6.73, -4.88, -12.43, -7.97, -8.19)

plot_tau_vs_clt(tau, clt_home_XG, clt_draw_XG, clt_away_XG, model_name = "XGBoost")
```

## CatBoost Bundesliga

```{r}
clt_home_BCB <- c(0.67, 2.49, 2.92, 5.92, 5.53, 7.23, 8.71, 7.2, 4.3, 0.51, 4.04, 4.56, 7.72, 5.39, 3.42, 4.73, 4.64, 5.14, 1.51)
clt_draw_BCB <- c(-15.98, -15.49, -19.64, -20.73, -29.38, -40.13, -54.01, -61.13, -58.74, -65.0, -53.68, -58.85, -86.34, -107.16, -158.87, -175.08, -153.24, -153.24,0)
clt_away_BCB <- c(-27.16, -26.64, -23.72, -23.75, -26.18, -22.41, -23.37, -27.45, -23.38, -23.24, -25.57, -17.75, -26.78, -26.22, -27.5, -22.47, -21.27, -16.04, -28.13)

plot_tau_vs_clt(tau, clt_home_BCB, clt_draw_BCB, clt_away_BCB, model_name = "CatBoost")
```

## LightGBM Bundesliga

```{r}
clt_home_BLG <- c(0.42, 1.26, 2.29, 3.1, 3.62, 6.43, 3.42, 6.01, 7.05, 1.03, 4.31, 7.05, 10.82, 4.83, 4.77, 6.26, 13.84, 1.07, -4.99)
clt_draw_BLG <- c(-17.51, -18.84, -16.0, -9.81, -13.57, -19.58, -31.73, -47.62, -52.16, -52.1, -52.6, -74.94, -63.88, -61.44, -153.24, -153.24, -153.24, -153.24, -100.0)
clt_away_BLG <- c(-26.74, -28.8, -26.99, -25.56, -30.02, -28.4, -26.93, -33.5, -30.72, -26.43, -23.25, -24.01, -20.91, -19.95, -27.49, -23.08, -17.82, -10.89, -17.43)

plot_tau_vs_clt(tau, clt_home_BLG, clt_draw_BLG, clt_away_BLG, model_name = "LightGBM")
```

## Linear Regression Bundesliga

```{r}
clt_home_BLR <- c(-4.73, -4.45, -1.54, -2.95, -2.85, 0.88, -0.7, -2.0, -6.3, -2.79, -7.06, -4.56, -7.86, -6.26, -9.6, -11.69, -14.46, -13.91, -12.73)
clt_draw_BLR <- c(-22.45, -30.77, -34.4, -32.61, -34.18, -37.18, -25.94, -39.17, -42.78, -50.81, -53.09, -67.0, -65.05, -54.86, -85.79, -76.27, -76.27, -105.53, -99.63)
clt_away_BLR <- c(-25.07, -25.73, -27.56, -32.58, -31.58, -36.52, -39.83, -38.98, -40.99, -38.03, -34.44, -41.61, -38.41, -35.74, -32.72, -37.17, -47.38, -45.84, -45.37)

plot_tau_vs_clt(tau, clt_home_BLR, clt_draw_BLR, clt_away_BLR, model_name = "Linear Regression")
```

## Neural Network Bundesliga

```{r}
clt_home_BNN <- c(-0.77, -0.33, -2.41, -2.85, -1.39, 1.99, 1.20, -0.03, 1.09, -1.17, -2.33, -1.28, 4.18, 5.44, 2.79, 0.59, 0.33, -7.35, -3.90)
clt_draw_BNN <- c(-13.39, -8.62, -15.55, -20.60, -20.22, -24.99, -25.91, -27.76, -31.20, -22.19, -36.16, -53.95, -60.44, -31.95, -7.13, 2.95, 35.34, 35.34, 550.00)
clt_away_BNN <- c(-25.61, -24.49, -24.01, -24.32, -28.60, -28.58, -23.70, -26.96, -25.52, -24.19, -25.09, -19.67, -19.13, -22.12, -30.11, -43.11, -44.13, -46.33, -50.42)

plot_tau_vs_clt(tau, clt_home_BNN, clt_draw_BNN, clt_away_BNN, model_name = "Neural Network")
```

## Random Forest Bundesliga

```{r}
clt_home_BRF <- c(2.40, 4.11, 4.25, 2.45, 2.48, 2.86, 5.19, 2.72, 6.20, 8.71, 12.95, 3.92, 3.87, 0.20, -2.95, -1.49, 2.96, 2.32, 0.67)
clt_draw_BRF <- c(-7.43, -15.53, -23.01, -22.17, -19.48, -42.29, -50.44, -53.98, -56.69, -54.35, -54.34, -53.35, -59.03, -85.07, -107.31, -142.90, -158.87, -175.08, -100.00)
clt_away_BRF <- c(-24.09, -25.38, -30.35, -33.24, -30.27, -30.76, -30.98, -27.62, -33.33, -33.41, -30.94, -31.34, -25.25, -23.32, -25.35, -27.83, -30.01, -39.07, -53.79)

plot_tau_vs_clt(tau, clt_home_BRF, clt_draw_BRF, clt_away_BRF, model_name = "Random Forest")
```

## XGBoost Bundesliga

```{r}
clt_home_BXG <- c(-0.23, -1.00, 1.49, 2.00, 4.61, 4.91, 3.85, 5.04, 3.47, 2.80, 2.24, 6.71, 12.11, 10.68, 6.47, 3.03, 7.08, -2.07, -4.53)
clt_draw_BXG <- c(-17.46, -17.04, -19.98, -13.36, -14.73, -40.13, -43.54, -43.70, -46.28, -42.83, -52.17, -56.53, -87.38, -54.23, -167.17, -153.24, -153.24, -153.24, 550.00)
clt_away_BXG <- c(-28.69, -28.80, -27.17, -25.05, -28.51, -28.11, -28.29, -29.78, -29.58, -27.16, -23.15, -21.15, -24.31, -23.28, -26.15, -19.37, -15.54, -9.52, -12.93)

plot_tau_vs_clt(tau, clt_home_BXG, clt_draw_BXG, clt_away_BXG, model_name = "XGBoost")
```

# Empirisk 95% fordeling

```{r}
plot_tau_vs_empirisk <- function(tau, emp_home, emp_draw, emp_away, model_name = "Model") {
  df <- data.frame(
    tau = tau,
    Hjemmesejr = emp_home,
    Uafgjort = emp_draw,
    Udebanesejr = emp_away
  )

  df_long <- tidyr::pivot_longer(df, cols = -tau, names_to = "Resultat", values_to = "Empirisk")

  ggplot(df_long, aes(x = tau, y = Empirisk, color = Resultat, shape = Resultat)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2.5) +
    scale_color_manual(values = c("blue", "red", "darkgreen")) +
    labs(title = paste("Empirisk 95% vs. τ —", model_name),
         x = expression(tau),
         y = "Empirisk 95% Nedre Grænse") +
    theme_minimal(base_size = 13) +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"),
          legend.position = "top") +
    coord_cartesian(ylim = c(-30, 15))
}
```

## CatBoost Premier League

```{r}
emp_home_CB <- c(-10.69, -12.36, -9.96, -11.98, -13.35, -12.43, -10.35, -10.64, -8.54,
              -11.52, -14.49, -16.30, -18.88, -19.43, -25.42, -27.45, -25.18, -27.38, -21.92)
emp_draw_CB <- c(-16.10, -18.87, -19.34, -17.75, -14.88, -12.68, -16.35, -12.72, -11.95,
              -35.93, -31.27, -30.89, -47.80, -63.43, -76.80, -61.33, -55.38, -42.00, -100.00)
emp_away_CB <- c(-2.07, -6.60, -2.96, -6.58, -4.55, -13.44, -10.89, -9.45, -10.65,
              -12.57, -13.74, -10.25, -12.65, -13.69, -16.40, -15.67, -23.45, -23.26, -23.61)
plot_tau_vs_empirisk(tau, emp_home_CB, emp_draw_CB, emp_away_CB, model_name = "CatBoost")
```

## LightGBM Premier League

```{r}
emp_home_LG <- c(-4.57, -3.62, -7.55, -7.18, -7.56, -11.24, -14.85, -16.57, -16.75, -18.17, -18.89, -18.78, -18.33, -13.87, -15.28, -16.92, -15.52, -17.34, -17.40)
emp_draw_LG <- c(-18.26, -16.28, -22.86, -28.26, -34.20, -37.68, -40.72, -32.15, -33.81, -50.08, -38.77, -30.88, -35.00, -34.46, -50.67, -100.00, -100.00, -100.00, -100.00)
emp_away_LG <- c(-0.36, -5.63, -7.77, -12.50, -10.81, -10.90, -8.72, -7.03, -7.16, -6.18, -3.99, 0.12, 4.10, 9.17, 8.04, 4.12, -0.68, -2.45, -8.60)

plot_tau_vs_empirisk(tau, emp_home_LG, emp_draw_LG, emp_away_LG, model_name = "LightGBM")
```

## Linear Regression Premier League

```{r}
emp_home_LR <- c(-9.03, -7.37, -10.9, -12.15, -11.45, -11.51, -9.5, -12.34, -9.07, -10.12, -10.34, -10.0, -6.78, -9.6, -14.0, -12.49, -10.37, -13.02, -16.76)
emp_draw_LR <- c(-17.22, -18.11, -14.7, -15.22, -16.87, -19.01, -18.35, -19.0, -15.41, -22.96, -25.01, -28.49, -38.61, -22.28, -24.78, -20.21, -15.55, -37.42, -68.26)
emp_away_LR <- c(-0.52, -0.81, -3.48, -6.16, -2.24, -1.31, -0.72, -0.1, -3.76, -12.44, -10.72, -10.51, -5.46, -4.72, -8.54, -17.62, -19.16, -19.32, -27.93)

plot_tau_vs_empirisk(tau, emp_home_LR, emp_draw_LR, emp_away_LR, model_name = "Linear Regression")
```

## Neural Network Premier League

```{r}
emp_home_NN <- c(-10.69, -12.36, -9.96, -11.98, -13.35, -12.43, -10.35, -10.64, -8.54,
              -11.52, -14.49, -16.30, -18.88, -19.43, -25.42, -27.45, -25.18, -27.38, -21.92)

emp_draw_NN <- c(-16.10, -18.87, -19.34, -17.75, -14.88, -12.68, -16.35, -12.72, -11.95,
              -35.93, -31.27, -30.89, -47.80, -63.43, -76.80, -61.33, -55.38, -42.00, -100.00)

emp_away_NN <- c(-2.07, -6.60, -2.96, -6.58, -4.55, -13.44, -10.89, -9.45, -10.65,
              -12.57, -13.74, -10.25, -12.65, -13.69, -16.40, -15.67, -23.45, -23.26, -23.61)


plot_tau_vs_empirisk(tau, emp_home_NN, emp_draw_NN, emp_away_NN, model_name = "Neural Network")
```

## Random Forest Premier League

```{r}
emp_home_RF <- c(-6.42, -8.0, -8.69, -10.66, -12.75, -16.06, -19.11, -20.75, -19.61, -18.91, -17.6, -16.48, -14.75, -16.94, -15.53, -13.91, -14.44, -12.93, -12.67)
emp_draw_RF <- c(-18.77, -23.71, -28.12, -24.7, -34.53, -38.94, -47.13, -61.79, -55.05, -45.03, -43.36, -43.21, -47.06, -49.62, -61.58, -61.33, -100.0, -100.0, -100.0)
emp_away_RF <- c(-4.09, -6.75, -10.18, -6.73, -1.89, -4.04, -2.23, -8.0, -8.7, -6.24, -8.1, -9.46, -7.57, -6.65, -6.09, -4.42, -11.42, -7.51, -7.39)

plot_tau_vs_empirisk(tau, emp_home_RF, emp_draw_RF, emp_away_RF, model_name = "Random Forest")
```

## XGBoost Premier League

```{r}
emp_home_XG <- c(-6.42, -8.0, -8.69, -10.66, -12.75, -16.06, -19.11, -20.75, -19.61, -18.91, -17.6, -16.48, -14.75, -16.94, -15.53, -13.91, -14.44, -12.93, -12.67)
emp_draw_XG <- c(-18.77, -23.71, -28.12, -24.7, -34.53, -38.94, -47.13, -61.79, -55.05, -45.03, -43.36, -43.21, -47.06, -49.62, -61.58, -61.33, -100.0, -100.0, -100.0)
emp_away_XG <- c(-4.09, -6.75, -10.18, -6.73, -1.89, -4.04, -2.23, -8.0, -8.7, -6.24, -8.1, -9.46, -7.57, -6.65, -6.09, -4.42, -11.42, -7.51, -7.39)

plot_tau_vs_empirisk(tau, emp_home_XG, emp_draw_XG, emp_away_XG, model_name = "XGBoost")
```

## CatBoost Bundesliga

```{r}
emp_home_BCB <- c(1.04, 2.95, 3.4, 6.6, 5.98, 7.74, 9.22, 7.91, 5.24, 1.16, 4.49, 4.95, 8.25, 6.01, 3.88, 5.29, 5.04, 5.24, 2.16)
emp_draw_BCB <- c(-15.59, -15.26, -19.17, -19.95, -28.88, -38.95, -52.46, -58.8, -55.91, -59.3, -45.59, -51.85, -63.89, -100.0, -100.0, -100.0, -100.0, -100.0,0)
emp_away_BCB <- c(-26.44, -26.01, -22.93, -22.54, -25.2, -21.32, -22.24, -26.01, -21.93, -21.29, -24.33, -16.8, -26.06, -25.55, -26.86, -21.96, -20.43, -15.26, -27.2)

plot_tau_vs_empirisk(tau, emp_home_BCB, emp_draw_BCB, emp_away_BCB, model_name = "CatBoost")
```

## LightGBM Bundesliga

```{r}
emp_home_BLG <- c(0.87, 1.89, 2.93, 3.73, 3.98, 7.01, 3.87, 6.66, 7.92, 1.27, 4.68, 7.18, 11.38, 4.95, 5.12, 6.67, 14.36, 1.28, -4.43)
emp_draw_BLG <- c(-17.03, -18.24, -15.43, -9.03, -12.69, -18.54, -30.49, -45.0, -49.02, -50.58, -43.94, -74.0, -65.79, -40.0, -100.0, -100.0, -100.0, -100.0, -100.0)
emp_away_BLG <- c(-26.33, -27.99, -25.92, -25.56, -28.82, -27.15, -25.88, -32.59, -30.07, -25.92, -22.48, -22.72, -19.99, -18.95, -26.05, -21.43, -16.28, -8.85, -17.32)

plot_tau_vs_empirisk(tau, emp_home_BLG, emp_draw_BLG, emp_away_BLG, model_name = "LightGBM")
```

## Linear Regression Bundesliga

```{r}
emp_home_BLR <- c(-4.27, -4.0, -1.16, -2.66, -2.72, 0.99, -0.4, -1.65, -6.01, -2.29, -6.83, -4.44, -7.26, -6.07, -8.98, -11.13, -13.68, -13.23, -11.74)
emp_draw_BLR <- c(-22.0, -30.09, -33.52, -32.2, -33.28, -35.99, -25.0, -37.38, -40.71, -47.5, -44.77, -60.61, -58.06, -48.0, -64.71, -53.85, -53.85, -100.0, -100.0)
emp_away_BLR <- c(-24.5, -24.94, -26.78, -31.44, -30.64, -35.08, -38.23, -36.94, -39.0, -35.74, -31.25, -40.94, -37.55, -35.18, -32.51, -35.87, -45.87, -44.48, -43.52)

plot_tau_vs_empirisk(tau, emp_home_BLR, emp_draw_BLR, emp_away_BLR, model_name = "Linear Regression")
```

## Neural Network Bundesliga

```{r}
emp_home_BNN <- c(-0.27, -0.21, -2.09, -2.45, -1.16, 2.38, 1.99, 0.58, 1.51, -0.45, -1.46, -0.61, 5.04, 6.68, 2.98, 0.99, 0.90, -6.85, -2.92)
emp_draw_BNN <- c(-13.07, -8.28, -14.84, -20.28, -19.65, -23.69, -24.23, -26.85, -29.54, -20.13, -32.76, -48.70, -63.89, -41.67, 20.00, 8.33, 116.67, 116.67, 550.00)
emp_away_BNN <- c(-25.34, -24.31, -23.67, -23.93, -27.89, -27.97, -23.01, -26.38, -24.95, -23.69, -23.83, -18.48, -17.42, -20.01, -27.78, -42.04, -42.99, -44.77, -48.03)

plot_tau_vs_empirisk(tau, emp_home_BNN, emp_draw_BNN, emp_away_BNN, model_name = "Neural Network")
```

## Random Forest Bundesliga

```{r}
emp_home_BRF <- c(2.66, 4.41, 4.58, 2.92, 2.92, 3.70, 5.69, 3.71, 6.67, 9.33, 13.67, 4.66, 4.74, 0.59, -2.73, -0.75, 3.82, 3.21, 1.24)
emp_draw_BRF <- c(-7.18, -14.99, -22.02, -21.42, -18.67, -40.58, -48.86, -51.41, -54.46, -51.67, -45.59, -43.18, -51.92, -66.67, -100.00, -100.00, -100.00, -100.00, -100.00)
emp_away_BRF <- c(-23.35, -24.56, -29.96, -32.79, -29.75, -30.29, -30.71, -27.04, -32.62, -33.15, -30.57, -30.75, -24.62, -22.99, -25.09, -27.35, -29.17, -37.94, -52.58)

plot_tau_vs_empirisk(tau, emp_home_BRF, emp_draw_BRF, emp_away_BRF, model_name = "Random Forest")
```

## XGBoost Bundesliga

```{r}
emp_home_BXG <- c(0.30, -0.68, 1.71, 2.75, 4.79, 5.59, 4.19, 5.74, 4.00, 3.34, 2.43, 6.98, 12.59, 11.07, 6.75, 3.47, 7.54, -1.64, -4.05)
emp_draw_BXG <- c(-17.04, -16.55, -19.42, -12.75, -13.86, -39.20, -42.12, -41.74, -43.06, -40.14, -43.94, -50.00, -66.67, -33.33, -100.00, -100.00, -100.00, -100.00, 550.0)
emp_away_BXG <- c(-28.03, -28.16, -26.55, -24.12, -27.41, -27.05, -27.01, -28.39, -29.00, -26.57, -22.42, -20.62, -23.36, -22.14, -24.70, -18.01, -14.38, -7.81, -12.00)

plot_tau_vs_empirisk(tau, emp_home_BXG, emp_draw_BXG, emp_away_BXG, model_name = "XGBoost")
```
